---
title: "lab03-yvonne-zhou"
author: "Yvonne Zhou"
date: "2/14/2019"
output: html_document
---

> What's the character delimiter?
Answer: ","

> Is there a row for column names?
Answer: There's no row for column names.But in the description of the data, there's information about each attributes.

> Are there any missing values? If so, how are they codified?
Answer: No. There is no missing values.

> What is the data type of each column?
Answer: They are nominal, continuous, continuous, continuous, continuous, continuous, continuous, continuous, integer.

```{r}
url <- "http://archive.ics.uci.edu/ml/machine-learning-databases/abalone/abalone.data"
abalone <- read.table(url, sep = ",")
```

```{r}
abalone <- read.table("abalone.data", sep = ",")

# take a peek of first rows
head(abalone)

# take a peek of last rows
tail(abalone)

# check data frame's structure
str(abalone, vec.len = 1)
```
```{r}
column_names <- c("Sex", "Length", "Diameter", "Height", "Whole", "Shucked", "Viscera", "Shell", "Rings")
column_types <- c("character", "real", "real", "real", "real", "real", "real", "real", "integer")

abalone = read.table("abalone.data", sep = ",", col.names = column_names, colClasses = column_types)
head(abalone)
str(abalone)
```

```{r}
abalone2 = read.csv("abalone.data", sep = ",")
head(abalone2)
str(abalone2)
```

```{r}
abalone10 = read.table("abalone.data", sep = ",", col.names = column_names, colClasses = column_types, nrows = 10)
head(abalone10)
str(abalone)
```

```{r}
abalone20 = read.table("abalone.data", sep = ",", col.names = column_names, colClasses = column_types, nrows = 10, skip = 10)
head(abalone20)
str(abalone)
```
> Read the documentation of read.table() about the argument colClasses. What happens when you specify the data-type of one or more columns as "NULL"? 
Answer: That column will be skipped.

```{r}
str(abalone)
summary(abalone)
head(abalone)
tail(abalone)
dim(abalone)
names(abalone)
colnames(abalone)
nrow(abalone)
ncol(abalone)
```

```{r}
use = abalone[-1]
a <- apply(use, 2, min)
a
b <- apply(use, 2, max)
b
c <- apply(use, 2, mean)
c
d <- apply(use, 2, sd)
d
```

```{r}
# first three rows
three_rows <- abalone[1:3, ]
three_rows
```

```{r}
# subset rows given a condition
# (length greater than 0.6)
gt <- abalone[abalone$Length > 0.6, ]
head(gt)
```

```{r}
length_diam <- abalone[ ,c('Length', 'Diameter')]
head(length_diam)
```

```{r}
five_rows <- abalone[1:5, ]
five_rows
```

```{r}
per_five_rows <- abalone[seq(1, nrow(abalone), by=5), ]
head(per_five_rows)
```

```{r}
last_five_rows <- abalone[seq(nrow(abalone) - 4, nrow(abalone), by=1), ]
last_five_rows
```

```{r}
height14 <- abalone[abalone$Height < 0.14, ]
head(height14)
```

```{r}
infant <- abalone[abalone$Sex == "I", ]
dim(infant)
```
```{r}
male_female <- abalone[(abalone$Sex == "M" | abalone$Sex == "F"), ]
dim(male_female)
```

```{r}
filter1 <- abalone[abalone$Rings > 25, c('Sex', 'Rings')]
filter1
```

```{r}
filter2 <- abalone[(abalone$Rings > 3 & abalone$Rings < 6), c('Sex', 'Rings', 'Diameter')]
head(filter2)
```
```{r}
# creating a small data frame
abies <- abalone[abalone$Sex == 'I', c('Length', 'Height', 'Diameter')]
abies$Ht_Len <- abies$Height / abies$Length
abies2 <- abies[order(abies$Length, decreasing = TRUE), ]
head(abies)
```

```{r}
babies <- abalone[abalone$Sex == 'I', ]
head(babies)
abies$product <- babies$Whole * babies$Shucked
abies3 = abies
abies3$log_height <- log(babies$Height)
abies3$log_length <- log(babies$Length)
head(abies)
head(abies3)
```
```{r}
filtered_abalone <- abalone[abalone$Height < 0.12, ]
#filtered_abalone
filtered_and_ordered_abalone <- 
  filtered_abalone[order(filtered_abalone$Height, decreasing = FALSE),]
head(filtered_and_ordered_abalone)
```

```{r}
highest_abalone <- abalone[order(abalone$Height, decreasing = TRUE), ]
top_five_highest_abalone <- highest_abalone[1:5, c('Sex', 'Diameter', 'Rings')]
top_five_highest_abalone

longest_abalone <- abalone[order(abalone$Length, decreasing = TRUE), ]
top_five_longest_abalone <- longest_abalone[1:5, c('Sex', 'Diameter', 'Rings')]
top_five_longest_abalone
```

```{r}
table_sex <- table(abalone$Sex)
barplot(table_sex)

hist(abalone$Diameter)
boxplot(abalone$Diameter, horizontal = TRUE)
```

```{r}
plot(abalone$Height)
#plot(abalone$Sex) #Error
plot(abalone$Height, abalone$Length)
#plot(abalone$Height, abalone$Length, abalone$Diameter) #Error
#plot(abalone$Sex, abalone$Length) #Error
#plot(abalone$Length, abalone$Sex) #Error
#Could only plot numeric vectors
```

```{r}
plot.default(-5:5, -5:5, type = "p")
points(0, 1, pch = 2)
points(0, 2, col = "blue")
points(0, 3, cex = 0.5)
plot.default(0, 1, xlab = "x-axis")
plot.default(0, 1, ylab = "y-axis")
plot.default(0, 1, main = "diagram")
plot.default(0, 1, sub = "021419")
```

