---
title: "warmup06-yvonne-zhou"
author: "Yvonne Zhou"
date: "3/24/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

```{r}
library(ggplot2)
```

#1) Future Value Fuction
@title future_value
@description calculate the future value of the amount of money after a few years
@param amount, rate, years
@return the amount of value that will return after a few years
```{r}
future_value <- function(amount, rate, years) {
  return(amount * (1 + rate) ** years)
}
```

```{r}
future_value(amount = 100, rate = 0.05, years = 1)
future_value(amount = 500, rate = 0.05, years = 5)
future_value(amount = 1000, rate = 0.05, years = 10)
```

#2) Future Value of Annuity
@title annuity
@description calculate the future value of annuity after a few years
@param contrib, rate, years
@return the annuity that will return after a few years
```{r}
annuity <- function(contrib, rate, years) {
  return(contrib * (((1 + rate) ** years) - 1) / rate)
}
```

```{r}
annuity(contrib = 200, rate = 0.05, years = 1)
annuity(contrib = 200, rate = 0.05, years = 2)
annuity(contrib = 200, rate = 0.05, years = 10)
```

#3) Future Value of Growing Annuity
@title growing_annuity
@description calculate the future value of growing annuity after a few years
@param contrib, rate, growth, years
@return the funture value of growing annuity that will return after a few years
```{r}
growing_annuity <- function(contrib, rate, growth, years) {
  return(contrib * (((1 + rate) ** years - (1 + growth) ** years) / (rate - growth)))
}
```

```{r}
growing_annuity(contrib = 200, rate = 0.05, growth = 0.03, years = 1)
growing_annuity(contrib = 200, rate = 0.05, growth = 0.03, years = 2)
growing_annuity(contrib = 200, rate = 0.05, growth = 0.03, years = 10)
```

#4) Investing Modalities
```{r}
no_contrib = c(1000)
fixed_contrib = c(1000)
growing_contrib = c(1000)
for (i in 1: 10) {
  no_contrib = append(no_contrib, future_value(1000, 0.05, i))
  fixed_contrib = append(fixed_contrib, future_value(1000, 0.05, i) + annuity(200, 0.05, i))
  growing_contrib = append(growing_contrib, future_value(1000, 0.05, i) + growing_annuity(200, 0.05, 0.03, i))
}
year = 0:10
modalities = data.frame(year, no_contrib, fixed_contrib, growing_contrib)
modalities
```

```{r}
ggplot(data = modalities) + 
  labs(x = "Years", y = "Amount of Money") +
  ggtitle("Comparison Between Three Models") +
  geom_line(aes(x = year, y = no_contrib, group = 1, color = "#FF6347")) + 
  geom_line(aes(x = year, y = fixed_contrib, group = 2, color = "blue")) + 
  geom_line(aes(x = year, y = growing_contrib, group = 3, color = "green")) +
  scale_color_manual(name  ="modality",
                    labels = c("no_contrib", "fixed_contrib", "growing_contrib"),
                    values = c("#FF6347", "#228B22", "#56B4E9")
                    ) +
  theme_light() +
  theme(plot.title = element_text(family = "Trebuchet MS", color = "#666666", face ="bold", size = 16, hjust = 0.5)) +
  theme(axis.title = element_text(family = "Trebuchet MS", color ="#666666", face ="bold", size = 12))
```

#5) Saving Simulation
```{r}
no_contrib_regular = c(10000)
no_contrib_highy = c(10000)
no_contrib_index = c(10000)
fixed_contrib_regular = c(10000)
fixed_contrib_highy = c(10000)
fixed_contrib_index = c(10000)
growing_contrib_regular = c(10000)
growing_contrib_highy = c(10000)
growing_contrib_index = c(10000)


for (i in 1: 15) {
  no_contrib_regular = append(no_contrib_regular, future_value(10000, 0.001, i))
  no_contrib_highy = append(no_contrib_highy, future_value(10000, 0.0225, i))
  no_contrib_index = append(no_contrib_index, future_value(10000, 0.065, i))
  
  fixed_contrib_regular = append(fixed_contrib_regular, future_value(10000, 0.001, i) + annuity(2000, 0.001, i))
  fixed_contrib_highy = append(fixed_contrib_highy, future_value(10000, 0.0225, i) + annuity(2000, 0.0225, i))
  fixed_contrib_index = append(fixed_contrib_index, future_value(10000, 0.065, i) + annuity(2000, 0.065, i))
  
  growing_contrib_regular = append(growing_contrib_regular, future_value(10000, 0.001, i) + growing_annuity(2000, 0.001, 0.04, i))
  growing_contrib_highy = append(growing_contrib_highy, future_value(10000, 0.0225, i) + growing_annuity(2000, 0.0225, 0.04, i))
  growing_contrib_index = append(growing_contrib_index, future_value(10000, 0.065, i) + growing_annuity(2000, 0.065, 0.04, i))
}

#no_contrib_regular
#no_contrib_highy
#no_contrib_index
#fixed_contrib_regular
#fixed_contrib_highy
#fixed_contrib_index
#growing_contrib_regular
#growing_contrib_highy
#growing_contrib_index
```

```{r}
years = 0:15
name = c("Year", "NoContribution", "FixedContribution", "GrowingContribution", "Rates")
regular = data.frame(years, no_contrib_regular, fixed_contrib_regular, growing_contrib_regular)
regular$rates = "1"
#regular = t(regular)
names(regular) = name
#regular

highy = data.frame(years, no_contrib_highy, fixed_contrib_highy, growing_contrib_highy)
highy$rates = "2"
#highy = t(highy)
names(highy) = name
#highy

index = data.frame(years, no_contrib_index, fixed_contrib_index, growing_contrib_index)
index$rates = "3"
names(index) = name
#index = t(index)
#index

ratenames <- c("1" = "regular savings", "2" = "high-yield savings", "3" ="index fund")

total = rbind(rbind(regular, highy), index)
total
```


```{r}
tt <- ggplot(data = total) +  
      geom_point(aes(x = Year, y = NoContribution, color = "#FF6347")) +
      geom_point(aes(x = Year, y = FixedContribution, color = "blue")) +
      geom_point(aes(x = Year, y = GrowingContribution, color = "green")) +
      geom_line(aes(x = Year, y = NoContribution, color = "#FF6347")) +
      geom_line(aes(x = Year, y = FixedContribution, color = "blue")) +
      geom_line(aes(x = Year, y = GrowingContribution, color = "green")) +
      facet_wrap(~Rates, labeller = as_labeller(ratenames)) +
      ylab("balance") +
      xlab("year") +
      labs(colour = "modality") +
      scale_color_manual(labels = c("no_contrib", "fixed_contrib", "growing_contrib"), values = c("#FF6347", "#228B22", "#56B4E9"))
tt
```
